Analysis

### 2022-08-16 analysis.qmd
Adjust iterations

fits <- dm %>% 
  select(outcome, year, country, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  mutate(
    dau = map2(
      data, outcome,
      ~brm(
        model_dau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 4000,
        data = .x,
        file = str_glue("models/brm-dau-{.y}")
      )
    ),
    mau = map2(
      data, outcome,
      ~brm(
        model_mau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 4000,
        data = .x,
        file = str_glue("models/brm-mau-{.y}")
      )
    )
  )
```

>>>>

fits <- dm %>% 
  select(outcome, year, country, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  mutate(
    dau = map2(
      data, outcome,
      ~brm(
        model_dau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 3000,
        data = .x,
        file = str_glue("models/brm-dau-{.y}")
      )
    ),
    mau = map2(
      data, outcome,
      ~brm(
        model_mau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 3000,
        data = .x,
        file = str_glue("models/brm-mau-{.y}")
      )
    )
  )
```
